### 2021-11-14 NSF2021/Description/specificaim1.tex
fixed typos in whole document

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent, which we solve with a
second-order Adams-Bashforth method. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

@@

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

The density~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

@@

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently when the number of particles is large.

@@

\subsubsection{Janus-particle self-assembly} 
Distinct morphologies can be obtained from 
the HAP model by shifting the boundary condition $g$.
Consider the linear case where $f(u) = u^2$.
This choice makes \eqref{eq:SL} a boundary value
problem for the screened-Laplace equation
and the solutions have a boundary layer structure that decays to $0$ in the
bulk with the decay length $\rho$.
We consider three kinds of boundary conditions
on particle $\Gamma_i$:
\begin{equation}
  \label{eq:bcs}
  \begin{tabular}{c|c|c}
     \text{(a)} & \text{(b)} & \text{(c)} \\
    \hline
    \rule{0pt}{4ex} 
      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
\end{tabular}
\end{equation}
  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
The normalizations, e.g. $(\pi r)^{-1/2}$, provide a uniform
surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
of radius $r$. 
The cases (b) and (c) are obtained by applying a vertical shift
and scaling to case (a), which amounts to changing one line of code. 
Using this setup, we simulate the dynamics of 100 particles with random
initial position and orientation.

@@

\begin{wrapfigure}[11]{r}{0.65\textwidth}
  \vspace{-10pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow is its director.}
\end{wrapfigure}

Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity three times as great
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
      (a)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Using the same initial configuration,
    particles self-assemble into distinct morphologies based
    on the boundary condition $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

\todo[inline]{Rationalize and citations for following} 
Finally, boundary condition \eqref{eq:bcs}(c) models 
a particle with oppositelly charged ends making the 
particle heads repel the tails \cite{MaRa76, Ma77}.
The particles initially form chains with their directors perpendicular to the
length of the chain. The equilibrium structure consists of particles
positioned on a square grid in a checkerboard pattern
Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
energy minimality and allows each particle to simultaneously coordinate
its head with the head of three other particles and its tail with the
tail of three other particles.

\begin{wrapfigure}[14]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
  }
\end{wrapfigure}
The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control particle surface properties independently, 
whereas these properties are often difficult to decouple in experiment
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density functions for
relative orientation of nearby particles.
The single peak and broad tails for the blue curve indicates a bilayer structure.
The bimodal red curve indicates multilamellar monolayers. Finally,
The yellow distribution has peaks at $\pm 45^{\circ}$ 
indicating a checkboard pattern. 
As another example, Janus particles
with uniform surface properties are costly or difficult to
manufacture.  Thus, we can replace the ideal boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function behaves as a normal distribution with variance
like $1/\kappa_i$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example. Collaboration with experimental groups will
use numerical methods to predict parameter regimes 
to control particle-particle interactions.
In Specific Aim 3, we discuss how to include ions and surface charge.

@@

\subsubsection{Hydrophobic forces as capillary wetting}
A natural generalization of the linear response potential $f(u) = u^2$
is a fourth-order, tilted double-well potential
$f(u) = a(u-u_0)^2(u-u_1)^2 + bu$.
Here, the order parameter $u$ is related to
the mean number of nearest neighbors
per water molecule \cite{GoHaKo94}.
The value $u_0$ gives the absolute minimum in the bulk
and $u_1$ gives a local minimum for the
tetrahadral water network found at hydrophobic surfaces.
Figure \ref{fig:CA}(a) illustrates a double-well potential
and Specific Aim 2 describes the numerical implementation issues.

\begin{wrapfigure}[29]{l}{1.8in}
  \vspace{-4pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} (a) The double well potential $u_0 =
  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
  and inexact Newton's methods.}
\end{wrapfigure}
Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example.
PI BQ has developed fast integral equation solvers for
the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
PI RR and colaborators launched the
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

The double-well formulation can potentially 
explain hydrophobic interaction over the full distance
regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
Motivated by capillary wetting, Gerhard
Gompper introduced the double-well model for one-dimensional
hydrophobic attraction \cite{GoHaKo94}.
The results improved on previous work~\cite{ErLjCl89,MaRa76},
but a realistic model of hydrophobic effect 
probably involves particle shapes in addition to distances of separation.
The key innovation in the model we propose is that when particles are
well-separated, the energetic cost for filling the interstitial region
with $u_0$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_0$-phases. This introduces a line tension for the phase transition
which is an effect not present in the one-dimensional model.

Some of the model parameters connect directly
%connect to long-range decay lengths and energy cost of creating
%hydrophobic-water interfaces with established ranges of
to well-established experimental values. Other
parameters, like the details of the well structure,
are less well-understood and must be fit to the measured data.
This improved model will allow us to more accurately 
simulate colloidal suspensions.
%The experimental data on hydrophobic attraction between 
%is well-established and the literature contains data for a number of
%solvents and hydrocarbon species.
%The experimental measurements
%are well-fit by a double exponential curve in the 10 to 100 nanometer range
%of separation. Below 10~nm, however, there is an amplification of force
%and the attraction follows a much steeper force law not accounted
%for by past phenomenoloical theories~\cite{Lin2005}.

>>>>

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. We then use a
second-order Adams-Bashforth method to update the particle configuration.
Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

@@

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

@@

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time-step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently when the number of particles is large.

@@

\subsubsection{Janus-particle self-assembly} 
Distinct morphologies can be obtained from 
the HAP model by shifting the boundary condition $g$.
Consider the linear case where $f(u) = u^2$.
This choice makes \eqref{eq:SL} a boundary value
problem for the screened-Laplace equation
and the solutions have a boundary layer structure that decays to $0$ in the
bulk with the decay length $\rho$.
We consider three kinds of boundary conditions
on particle $\Gamma_i$:
\begin{equation}
  \label{eq:bcs}
  \begin{tabular}{c|c|c}
     \text{(a)} & \text{(b)} & \text{(c)} \\
    \hline
    \rule{0pt}{4ex} 
      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
\end{tabular}
\end{equation}
  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
of radius $r$. 
The cases (b) and (c) are obtained by applying a vertical shift
and scaling to case (a), see Figure \ref{fig:bcs}.
Using this setup, we simulate the dynamics of 100 particles with random
initial position and orientation.

@@

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}

Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
      (a)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

\begin{wrapfigure}[14]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
  }
\end{wrapfigure}
Finally, boundary condition \eqref{eq:bcs}(c) models 
a \hl{particle with oppositelly charged ends} making the 
particle heads repel the tails \cite{MaRa76, Ma77}.
The particles initially form chains with their directors perpendicular to the
length of the chain. The equilibrium structure consists of particles
positioned on a square grid in a checkerboard pattern
Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
energy minimality and allows each particle to simultaneously coordinate
its head with the head of three other particles and its tail with the
tail of three other particles.

The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control surface properties independently, 
which can be difficult to accomplish experimentaly 
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density function for 
relative orientation of adjacent particles
for the three boundary condition cases:
(a) is unimodal with a peak at $\theta = 0$,
(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
This kind of information can be used as an indicator
of the collective morphology. As another example,
it is costly or difficult to manufacture
Janus particles with uniform shape.
Thus, we can replace the idealistic boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function is asymptotic to a normal distribution with variance
like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example. \hl{Collaboration with experimental groups will
use numerical methods to predict parameter regimes 
to control particle-particle interactions.}
In Specific Aim 3, we discuss how to include ions and surface charge.

@@

\subsubsection{Hydrophobic forces with double-well potential}
A natural generalization of the potential $f(u) = u^2$
is a fourth-order, asymmetric double-well potential
$f(u) = a(u-u_0)^2(u-u_1)^2 + c(u-u_0)^2 + bu$.
Here, the order parameter $u$ is related to
the mean number of nearest neighbors
per water molecule \cite{GoHaKo94}.
The value $u_0$ gives the absolute minimum in the bulk
and $u_1$ gives a local minimum at hydrophobic surfaces.
Figure \ref{fig:CA}(a) illustrates a double-well potential
and Specific Aim 2 describes the numerical implementation issues.

\begin{wrapfigure}[29]{l}{1.8in}
  \vspace{-4pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} (a) The double well potential $u_0 =
  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
  and inexact Newton's methods.}
\end{wrapfigure}
Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example.
PI BQ has developed fast integral equation solvers for
the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
PI RR has experience in the 
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

The double-well formulation can potentially 
explain hydrophobic interaction over the full distance
regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
Motivated by capillary wetting, Gerhard
Gompper introduced the double-well model for one-dimensional
hydrophobic attraction \cite{GoHaKo94}.
The results improved on previous work~\cite{ErLjCl89,MaRa76},
but a realistic model of hydrophobic effect 
probably involves particle shapes in addition to distances of separation.
The key innovation in the model we propose is that when particles are
well-separated, the energetic cost for filling the interstitial region
with $u_1$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_1$-phases. This introduces a line tension for the phase transition
which is an effect not present in the one-dimensional model.

Some of the model parameters connect directly
%connect to long-range decay lengths and energy cost of creating
%hydrophobic-water interfaces with established ranges of
to well-established experimental values. Other
parameters, like the details of the well structure,
are less well-understood and must be fit to the measured data.
This improved model will afford greater physical accuracy to
our simulations.
%The experimental data on hydrophobic attraction between 
%is well-established and the literature contains data for a number of
%solvents and hydrocarbon species.
%The experimental measurements
%are well-fit by a double exponential curve in the 10 to 100 nanometer range
%of separation. Below 10~nm, however, there is an amplification of force
%and the attraction follows a much steeper force law not accounted
%for by past phenomenoloical theories~\cite{Lin2005}.
